FHJ: A Formal Model for Resolving Unintended Conflicts in Multiple Inheritance

### 2017-06-15 Aplas17/sections/Formalization.tex
small fix

\section{Formalization}~\label{sec:formalization}

In this section, we present a formalization of our \MIM{} calculus, based on
a minimal subset of Java 8 interfaces following Featherweight Java style~\cite{Igarashi01FJ}.
The syntax, typing rules and small-step
semantics are included below.

>>>>

\section{Formalization}~\label{sec:formalization}
In this section, we present the formal model \MIM{}, short for 
\emph{\textbf{F}eatherweight \textbf{H}irarchical \textbf{J}ava} , based on
a minimal subset of Java 8 interfaces following Featherweight Java style~\cite{Igarashi01FJ}.
The syntax, typing rules and small-step semantics are included below.
